The Birth of a Galaxy: Primordial Metal Enrichment and Population II Stellar Populations

### 2010-10-31 science_ms.tex
Minor change.
Shortened abstract to 125 words.

\title{The Birth of a Galaxy: Population III Metal Enrichment and
  Population II Stellar Populations}

@@

\begin{sciabstract}
  Supernova explosions from the first stars in the universe, which are
  predicted to be very massive, chemically enriched the intergalactic
  medium, originally a primordial mix of hydrogen and helium.  A
  fraction of these metals propagate into star-forming regions,
  providing more efficient cooling mechanisms and, in turn, increasing
  gaseous fragmentation in the first stellar clusters.  Here, we
  report on the birth of two high-redshift dwarf galaxies in a
  cosmological radiation hydrodynamics simulation.  We find that only
  one supernova is sufficient to enrich the nearby star-forming gas
  with a floor of 1/1,000 of the solar metallicity ratio, preventing
  any further metal-free star formation within 10 kpc of the past
  explosion.  This provides a natural explanation for the observed
  floor on damped Lyman alpha (DLA) systems metallicities reported in
  the literature, which is of this order.  We follow the entire star
  formation history of these galaxies, providing robust models to
  interpret the stellar populations of nearby dwarf galaxies and
  future observations of high-redshift dwarf galaxies.
\end{sciabstract}

@@

The evolution of the stellar and gas metallicity of both halos are
illustrated in Figure \ref{fig:evo}b.  PISNe from Pop III stars enrich
the nearby IGM out to a radius of 10 kpc and provides a metallicity
floor of $[Z_3/H] \sim -3$.  The metallicity from Pop II SNe initially
enrich the ISM of both halos to an average $[\bar{Z}_2/H]$ between
--3.5 and --3.

>>>>

\title{The Birth of a Galaxy: Primordial Metal Enrichment and
  Population II Stellar Populations}

@@

\begin{sciabstract}
  Supernova explosions from the first stars in the universe, which are
  predicted to be very massive, chemically enriched the intergalactic
  medium, providing the necessary elements for forming the first
  galaxies.  We report on the birth of two high-redshift dwarf
  galaxies in a cosmological radiation hydrodynamics simulation.  We
  find that only one supernova is sufficient to enrich the nearby
  star-forming gas with a floor of 1/1,000 of the solar metallicity
  ratio, preventing any metal-free star formation within 10 kpc of the
  past explosion.  This provides a natural explanation for the
  observed floor on damped Lyman alpha systems metallicities.  We
  follow the entire star formation history of these galaxies,
  providing robust models to interpret the stellar populations of
  nearby dwarf galaxies and future observations of high-redshift dwarf
  galaxies.
\end{sciabstract}

@@

The evolution of the stellar and gas metallicity of both halos are
illustrated in Figure \ref{fig:evo}b.  PISNe from Pop III stars enrich
the nearby IGM out to a radius of 10 kpc and provides a metallicity
floor of $[Z_3/H] \sim -3$.  Ejecta from Pop II SNe initially enrich
the ISM of both halos to an average $[\bar{Z}_2/H]$ between --3.5 and
--3.
